Testing the precision of Bangla Communication Scale: Item Response Theory Guided Analysis

### 2022-02-02 manuscript.Rmd
Introduction part updated

affiliation:
  - id            : "1"
    institution   : "Department of Educational and Counselling Psychology,University of Dhaka"
  - id            : "2"
    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
  - id            : "*"
    institution   : "Joint first author"

@@

Communication is a complex behaviour of exchanging information among individuals combining physical and mental events. [@tanner2006advanced]. Communication plays a central role among adolescents in developing self-identity, social relationships and creates the foundation of collective social activity [@haslett1989children].

@@

Understanding the communication skills among the adolescents is vital as it is considered as the "key skill" in the education [@thurlow2001talkin]. To promote better understanding of subject contents assessing the communication skill among adolescents is highly required. For this purpose "Communication Skill" sub-skill set [@barkman2002four]  was developed in 2002 as a part of The  National  On-line  Youth  Life  Skills  Evaluation System [@mincemoyer2005measuring] and since then it has been extensively used .

# Study 1: Translations and Factor Structure

Our first study had two objectives. First, we translated the English communication scale to Bangla language. Second, to identified the latent structure of the Bangla Communication Scale (BCS) using Exploratory Factor Analysis (EFA)

## Methods

@@

A cross-sectional survey was used to collect data from a large sample of students of grade 8-12 (n = `r nrow(efa.data)`) from 8schools following convenience sampling method. T. For estimating the sample size for the CFA we followed the N:q rule [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]  which required 10 participants per parameters for trustworthiness of the result. Our sample size exceeds the requirement. Among `r nrow(efa.data))` participants, `r female[1,2]` were female aged between `r female[2,8]` to `r female[2,9]` years (`r round(female[2,3],2)`±`r round(female[2,4],2)`). `r male[1,2]`  were male with an age range between `r male[2,8]` participants `r male[2,9]` years (`r round(male[2,3],2)`±`r round(male[2,4],2)`). `r desc_tibble [4,2]` participants belonged to middle socio-economic status. `r desc_tibble [3,2]` and `r desc_tibble [5,2]` participants belonged to lower and upper socio-economic status-respectively.

## Procedure
Prior to data collection necessary authorization from school's authority and assent from the participating were obtained. Data collection was commenced between November 2021 to January 2022. The data collection took place in the classroom where students were at first briefed about 'communication skill'. Next. they filled up their sociademographics information and responded to our Bangla Communication Scale. All personal information (name, school,class) was codified and encrypted, producing a anonymous database.

@@

@@

#Histogram
#psych::multi.hist(EFA.data[,sapply(EFA.data, is.numeric)])

# Univariate normality

#creating normality function
shapiro_test_df <- function(df, bonf= TRUE, alpha= 0.05) {
  l <- lapply(df, shapiro.test)
  s <- do.call("c", lapply(l, "[[", 1))
  p <- do.call("c", lapply(l, "[[", 2))
  if (bonf == TRUE) {
    sig <- ifelse(p > alpha / length(l), "H0", "*")
  } else {
    sig <- ifelse(p > alpha, "H0", "*")
  }
  return(list(statistic= s,
              p.value= p,
              significance= sig,
              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction",
                             "Shapiro-Wilks test without Bonferroni Correction")))
}

Shapiro.efa <- shapiro_test_df(efa.data)

efa.normality.tab = matrix(nrow = 48, ncol = 2)
rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(efa.normality.tab) <- my.item.names
colnames(efa.normality.tab) <- c("statistic", "p")

efa.normality.tab[,1] <- apa(Shapiro.efa$statistic,2,T)
efa.normality.tab[,2] <- apa(Shapiro.efa$p.value,2,T)

efa.normalityprefix <- efa.normality.tab[,1]
efa.normalitysufix <- Shapiro.efa$significance
efa.normality.stat <- paste(efa.normalityprefix,efa.normalitysufix, sep = "" )

# Multivariate Normality
mardia <- psych::mardia(efa.data, na.rm = T, plot =F)

# Descriptive Stats
Descriptives <- psych::describe(EFA.data)
alpha <- psych::alpha(EFA.data,check.keys=TRUE)
Item.total <- alpha$item.stats

Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,T))

colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(Des.combined) = (my.names)

decriptives <- tabledown::des.tab(efa.data)
```

## Item Analysis
`

```{r Cronbach, results='asis', width = 60}
Cron.bach <- psych::alpha(efa.data,check.keys=TRUE) 
Cron.bach$total %>% 
  knitr::kable(caption = "Alpha", digits = 2) %>% 
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)
Cron.bach$alpha.drop %>% 
  knitr::kable(caption = "Alpha value if item is dropped", digits = 2) %>% 
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)

@@

reduced.model.2F.2 <- dplyr::select(EFA.data ,
                                    -c( CS07, CS13, CS16, CS05, CS10, CS19, CS03, CS02, CS09, CS23, CS17, CS04))

fa.2F.3 <- fa(r=correlations.red.2F.2$rho, nfactors = 2, fm= "pa",rotate ="promax",
              residuals = TRUE, SMC = TRUE, max.iter = 500 )

@@

png(filename="Manuscript.figures/CFAplot.png", 
    type="cairo",
    units="in", 
    width=12, 
    height=12, 
    pointsize=12, 
    res=1200)
semPaths (fit.1 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="OpenMx",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =8,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          #exoCov = T,
          centerLevels = T,
          #edge.color="black",
          label.scale=T,
          label.cex=1.2, #Font of factor and item name
          residuals=FALSE,
           #exoVar=FALSE,
          #fixedStyle=6, #Style of arrow (guide item)
          #freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

```{r Shortcut Invariance}
invariance.data <- cfa.data.full[, c(3, 6:28)]
invariance.data <- na.omit(invariance.data )
library("semTools")
invariance.model <- measurementInvariance(model = model.1,
                                          data = invariance.data,
                                          group = "Gender",                                                                         estimator = "WLSMV",
                                          strict = T)
invariance.model[[1]] #configural Invariance
invariance.model[[2]] # loading, weak, metric
invariance.model[[3]] # intercept, strong, scaler
invariance.model[[4]] # residual, strict
invariance.model[[5]] # means, structural invariance
```

```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis. By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.",  out.height='100%', warning=FALSE}

@@

```{r}
irt.data <- na.omit(irt.data)
irt.data.1 <- irt.data %>% 
  dplyr::select( CS03, CS04, CS06, CS07,CS08,CS10,CS11,    CS12, 
                 CS13,CS14,CS15,CS17, CS18, CS19, CS20 ,CS21, CS22)

@@

@@

@@

ICC <- cowplot::plot_grid(item03, item04, item06, item07, item08, 
                   item10, item11, item12, item13, item14, item15,  item17, item19,
                   item20, item21, 
                      labels = "AUTO",
                     ncol=4,  
                    label_size = 15, 
                     align = "v")

ggsave("Figures/ICC.png",ICC , width = 12, height = 12, dpi = 600, bg = "white")

@@

good.info <- cowplot::plot_grid( item6.iic1, item7.iic1, item11.iic1, item12.iic1, item14.iic1, item15.iic1 , item18.iic1, item19.iic1, item20.iic1, item21.iic1, item22.iic1, 
                                 labels = "AUTO",ncol=3, label_size = 15,align = "v")

ggsave("Figures/good.info.png",good.info, width = 12, height = 8, dpi = 600, bg = "white")

test.info <- tabledown::ggtestinfo(irt.data,fit)+ apatheme+geom_line(colour = "black", size=1.5)+geom_area(fill ="palegreen4" )+geom_vline(xintercept = -3, colour ="black")+
  geom_vline(xintercept = .5, colour ="black")
library(plotly)
info.p <- plotly::ggplotly(test.info)

@@

```{r IRT2, include}

irt.2 <- dplyr::select(EFA.data, -c(CS01,CS02,CS03,CS04, CS05,CS08, CS09, CS10, CS13, CS16, CS17,CS23))

fit2 <- mirt(irt.2, model = 1, itemtype = 'graded', 
               SE = TRUE, Se.type = 'MHRM',
               technical = list(NCYCLES = 10000))

occ <- plot(fit2, facet =T, type= "trace")

# Model Parameters ####
params2 <- coef(fit2, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
items2 <- data.frame(params2$items)
se2 <- coef(fit2, printSE = TRUE)

# Model Fit (degrees of freedom too low to check model fit)
model2 <- as.data.frame(M2(fit2))

#Item fit
item.fit2<- itemfit(fit2, fit_stats = c("S_X2",  "infit"),
                                  impute=10)

#Identifying Missfit items based on RMSEA Value
item_misfits2 <- subset(item.fit2, RMSEA.S_X2 >= .06)

## Creating IRT table
item.fit3 <- item.fit2[,-c(1,2,4)] 
colnames(item.fit3) <- c("Outfit", "Infit", "S-Chi-square", "df", "RMSEA", "p")

IRT.details <- cbind(items2 ,item.fit3)

# Person Fit ####
personfit2 <- personfit(fit2) 
personfit_model_misfits2 <- subset(personfit2, Zh < -2)
rownames(personfit_model_misfits2)
nrow(personfit_model_misfits2)

person <- ggplot(personfit2, aes(x=Zh)) + geom_histogram(binwidth=.5,col=I("black"),fill="palegreen4")+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics")+apatheme + xlim(-4,2)+
   scale_y_continuous(limits = c(0, 40), expand = expand_scale(mult = c(0, 0.1)))

annotation.1 <- data.frame(
   x = (-3.1),
   y = (20),
   label = ("Most of the participants
        are within the guidline")
)

per.anno <-person + geom_label(data=annotation.1, aes( x=x, y=y, label=label),                 , 
           color="orange", 
           size=5 , angle=45, fontface="bold" )

ggsave("Figures/person.png",per.anno , width = 12, height = 8, dpi = 600, bg = "white")

OCC2 <- plot(fit2, type = "trace", facet =T, main = "Communication Scale OCC")
info2 <- plot(fit2, type = "infoSE", main = "Communication Scale")
iteminfo2 <- plot(fit2, type = "infotrace", 
                    facet_items = T, main = "Communication Scale")

##Test Info
info <- tabledown::ggtestinfo(irt.2, fit2)+apatheme+geom_line(colour = "black", size=1.5)+geom_area(fill ="palegreen4" )+geom_vline(xintercept = -3, colour ="black")+
  geom_vline(xintercept = .5, colour ="black")
library(plotly)
info.p <- plotly::ggplotly(info)

annotation <- data.frame(
   x = c(-4.2,1.5),
   y = c(4.5,4.3),
   label = c("Theta = -3", "Theta =.5")
)

info.anno <- info + geom_label(data=annotation, aes( x=x, y=y, label=label),
           color="orange", 
           size=7 , angle=45, fontface="bold" )

ggsave("Figures/TIC.png",info.anno  , width = 12, height = 8, dpi = 600, bg = "white")

#conditional reliability
library(latticeExtra)
library(directlabels)
font.settings <- list(
  font = 1,
  cex = 6,
  fontfamily = "sans")

@@

reliability.focused <- plot(fit2, type = 'rxx', theta_lim = c(-4, 2), 
      main="Conditional Reliability Plot", par.settings=c(apa.latice),col.line = "#E69F00",lwd = 3.5 )

marginal.rel2 <- marginal_rxx(fit2)

#scale characteristics curve
scale2 <- plot(fit2, type = 'score', theta_lim = c(-6, 6), main = "")

@@

```{r conrel-print, include=F}
##
png(filename="Figures/conrel.png", 
    type="cairo",
    units="in", 
    width=12, 
    height=8, 
    pointsize=12, 
    res=300)
plot(fit2, type = 'rxx', theta_lim = c(-6, 6), 
      main="", par.settings=c(apa.latice),col.line = "#E69F00",lwd = 3.5, cex =2.5 )+
  layer(panel.abline(v = -4, colour = "red",panel=panel.filled_smooth))+
  layer(panel.abline(v = 1.5))

@@

```{r dif}
library("lordif")
gender <- as.data.frame(data$Gender)
colnames(gender) <- "Gender"
gender$Gender <- as.factor(gender$Gender)
irt.data <- na.omit(irt.data)
communication <- sem.data[,c(2:24)]
dif.data <- cbind(gender, communication)
dif.data <- na.omit(dif.data)
dif.data.full <- as.data.frame(dif.data)
DIF <- lordif(as.data.frame(irt.data), group = dif.data.full$Gender, criterion = "Chisqr")

@@

val.data<- validity.data.full %>% 
  dplyr::select( CS03, CS04, CS06, CS07,CS08,CS10,CS11,    CS12, 
                 CS13,CS14,CS15,CS17, CS18, CS19, CS20 ,CS21, CS22) %>% 
  rowwise() %>% 
  mutate(Total_communication = sum(across(starts_with("CS")), na.rm = T))

@@

## Material

## Procedure

## Data analysis
We used `r cite_r("references.bib")` for all our analyses.

>>>>

affiliation:
  - id            : "1"
    institution   : "Department of Educational and Counselling Psychology,University of Dhaka"
  - id            : "2"
    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"

@@

Communication is a complex behaviour of exchanging information among individuals [@tanner2006advanced]. Communication plays a central role among adolescents in developing self-identity, social relationships and creates the foundation of collective social activity [@haslett1989children; @conti2008emotional; @spencer2013language]. Inadequate communication skill may cause poor peer relationship resulting long-term socio-emotional difficulties including social anxiety, stress, low self-esteem and poor academic performance [@brinton2004social; @reed2020relative].

@@

Understanding the adolescents' communication skill  vital as it is considered as the "key skill" in the education [@thurlow2001talkin] and employment market [@olszewski2017training]. In the western society, adolescents are now facing high unemployment [@lindsay2014employers]. Lack of adequate communication skill is one of the root causes of this high unemployment [@lindsay2014employers]. Similarly, lack of proper communication skill often promotes the propensity of anti-social behaviours and risk of exclusion from schools [@clegg2009language; @conti2004social].

To promote better understanding of subject contents assessing the communication skill among adolescents is highly required. For this purpose "Communication Skill" sub-skill set [@barkman2002four]  was developed in 2002 as a part of The  National  On-line  Youth  Life  Skills  Evaluation System [@mincemoyer2005measuring] and since then it has been extensively used [@fitzpatrick2005life].

This study has two objectives: (a) To explore and validate the latent construct of "Bangla Communication Scale" using (b) To gather concurrent validity evidence (c) To increase the precision of the scale usining Item Response Theory guided analysis
## Methods

@@

A cross-sectional survey was used to collect data from a large sample of students of grade 8-12 (n = `r nrow(efa.data)`) from 8 schools following convenience sampling method. T. For estimating the sample size for the CFA we followed the N:q rule [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]  which required 10 participants per parameters for trustworthiness of the result. Our sample size exceeds the requirement. Among `r nrow(efa.data)` participants, `r female[1,2]` were female aged between `r female[2,8]` to `r female[2,9]` years (`r round(female[2,3],2)`±`r round(female[2,4],2)`). `r male[1,2]`  were male with an age range between `r male[2,8]` participants `r male[2,9]` years (`r round(male[2,3],2)`±`r round(male[2,4],2)`). `r desc_tibble [4,2]` participants belonged to middle socio-economic status. `r desc_tibble [3,2]` and `r desc_tibble [5,2]` participants belonged to lower and upper socio-economic status-respectively.

## Procedure
Prior to data collection necessary authorization from school's authority and assent from the participating were obtained. Data collection was commenced between November 2021 to January 2022. The data collection took place in the classroom where students were at first briefed about 'communication skill'. Next. they filled up their soci-demographics information and responded to our Bangla Communication Scale. All personal information (name, school,class) was codified and encrypted, producing a anonymous database.

@@

```{r, gtfig, include =F}

@@

decriptives <- tabledown::des.tab(efa.data)
colnames(decriptives) = c("Items","Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")

```{r}
apa_table(decriptives)
```

## Item Analysis

```{r Cronbach, include=FALSE, results='asis'}
Cron.bach <- psych::alpha(efa.data,check.keys=TRUE) 
Cron.bach$total %>% 
  knitr::kable(caption = "Alpha", digits = 2) %>% 
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)
Cron.bach$alpha.drop %>% 
  knitr::kable(caption = "Alpha value if item is dropped", digits = 2) %>% 
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)

@@

```{r eval=FALSE, include=FALSE}
model.1 <- "F1 =~ CS15 + CS22+CS20+CS14+CS18+CS13+CS06+CS10
            F2 =~ CS19+CS04+CS17+CS12+CS08+CS07"
fit.1 <- cfa(model.1, data = cfa.data, ordered = names(cfa.data),estimator = "WLSMV")

## Selected Fit measures 
fit.measures.1 <- fitmeasures (fit.1,c("gfi", "agfi", "nfi","rfi", 
                       "cfi","tli",
                       "rmsea", "rmsea.ci.lower", "rmsea.ci.upper","srmr"))
reliability1 <- semTools::reliability(fit.1, return.total = T)

@@

png(filename="figures/CFAplot.png", 
    type="cairo",
    units="in", 
    width=6, 
    height=6, 
    pointsize=12, 
    res=1200)
semPaths (fit.1 , 
          what= "std",
          #"hide", #(hides coefficeits)
          #whatLabels = "std",
          intercepts = F,
          style ="OpenMx",
          #residScale = 6,
          theme = "colorblind",
          nCharNodes = 0,
          reorder =T,
          rotation =2,
          layout ="tree",
          cardinal = T,
          curvePivot =T,
          sizeMan =8,#items length
          sizeMan2 = 2,#items
          sizeLat = 12,#factors
          thresholds = FALSE,
          equalizeManifests =F,
          fade = FALSE,
          edge.label.cex = .8,
          #exoCov = T,
          centerLevels = T,
          #edge.color="black",
          label.scale=T,
          label.cex=1.2, #Font of factor and item name
          residuals=FALSE,
           #exoVar=FALSE,
          #fixedStyle=6, #Style of arrow (guide item)
          #freeStyle=1#Style of arrow (other item), #XKCD = TRUE

@@

```{r Shortcut Invariance, eval=FALSE, include=FALSE}
invariance.data <- cfa.data.full[, c(3, 6:28)]
invariance.data <- na.omit(invariance.data )
library("semTools")
invariance.model <- measurementInvariance(model = model.1,
                                          data = invariance.data,
                                          group = "Gender",                                                                         estimator = "WLSMV",
                                          strict = T)
invariance.model[[1]] #configural Invariance
invariance.model[[2]] # loading, weak, metric
invariance.model[[3]] # intercept, strong, scaler
invariance.model[[4]] # residual, strict
invariance.model[[5]] # means, structural invariance
```

```{r figcfa, fig.cap = "CFA Plot.", warning=FALSE}

@@

```{r, include =F}
irt.data <- na.omit(irt.data)
irt.data.1 <- irt.data %>% 
  dplyr::select( CS03, CS04, CS06, CS07,CS08,CS10,CS11, CS12, 
                 CS13,CS14,CS15,CS17, CS18, CS19, CS20 ,CS21, CS22)

@@

## Creating IRT table
item.fit2 <- item.fit[,c(4,6,11,12,13,14)] 
colnames(item.fit2) <- c("Standardized Outfit", "Standardized Infit", "S-Chi-square", "df", "RMSEA", "p")

IRT.details <- cbind(items ,item.fit2)

@@

person <- ggplot(personfit, aes(x=Zh)) + geom_histogram(binwidth=.5,col=I("black"),fill="palegreen4")+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics")+apatheme + xlim(-4,2)+
   scale_y_continuous(limits = c(0, 40), expand = expand_scale(mult = c(0, 0.1)))

# annotation.1 <- data.frame(
#    x = (-3.1),
#    y = (20),
#    label = ("Most of the participants
#         are within the guidline")
# )
# 
# per.anno <-person + geom_label(data=annotation.1, aes( x=x, y=y, label=label),                 , 
#            color="orange", 
#            size=5 , angle=45, fontface="bold" )

ggsave("Figures/person.png",person , width = 12, height = 8, dpi = 600, bg = "white")

@@

ICC <- cowplot::plot_grid(item03, item04, item06, item07, item08, 
                   item10, item11, item12, item13, item14, item15,  item17, item18, item19,
                   item20, item21, item22,
                      labels = "AUTO",
                     ncol=3,  
                    label_size = 15, 
                     align = "v")

ggsave("Figures/ICC.png",ICC , width = 12, height =14, dpi = 600, bg = "white")

```{r figICC, eval=FALSE, fig.cap="Option Charecteritics Curve.", warning=FALSE, include=FALSE, out.height='100%'}

knitr::include_graphics("Figures/ICC.png", dpi =600)

@@

# good.info <- cowplot::plot_grid( item6.iic1, item7.iic1, item11.iic1, item12.iic1, item14.iic1, item15.iic1 , item18.iic1, item19.iic1, item20.iic1, item21.iic1, item22.iic1, 
#                                  labels = "AUTO",ncol=3, label_size = 15,align = "v")
# 
# 
# ggsave("Figures/good.info.png",good.info, width = 12, height = 8, dpi = 600, bg = "white")

test.info <- tabledown::ggtestinfo(irt.data.1, fit)+ apatheme+geom_line(colour = "black", size=1.5)+geom_area(fill ="#E64B3599" )
# +geom_vline(xintercept = -3, colour ="black")+
#   geom_vline(xintercept = .5, colour ="black")
ggsave("Figures/TIC.png",test.info , width = 6, height = 4, dpi = 600, bg = "white")

library(plotly)
info.p <- plotly::ggplotly(test.info)

@@

```{r figTIC, fig.cap = "TIC.",  out.height='100%', warning=FALSE}

knitr::include_graphics("Figures/TIC.png", dpi =600)

```{r conrel-print, include=F}
##
png(filename="Figures/conrel.png", 
    type="cairo",
    units="in", 
    width=12, 
    height=2, 
    pointsize=12, 
    res=300)
library(latticeExtra)
library(directlabels)
font.settings <- list(
  font = 1,
  cex = 6,
  fontfamily = "sans")

@@

 plot(fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="Conditional Reliability Plot", par.settings=c(apa.latice),col.line = "#E69F00",lwd = 3.5 )

```{r figconrel, fig.cap = "Conditional Reliability.",  out.height='100%', warning=FALSE}

knitr::include_graphics("Figures/conrel.png", dpi =600)

@@

@@

```{r dif, eval=FALSE, include=FALSE}
library("lordif")
gender <- as.data.frame(data$Gender)
colnames(gender) <- "Gender"
gender$Gender <- as.factor(gender$Gender)
irt.data <- na.omit(irt.data)
communication <- sem.data[,c(2:24)]
dif.data <- cbind(gender, communication)
dif.data <- na.omit(dif.data)
dif.data.full <- as.data.frame(dif.data)
DIF <- lordif(as.data.frame(irt.data), group = dif.data.full$Gender, criterion = "Chisqr")

@@

val.data<- validity.data.full %>% 
  dplyr::select( CS03, CS04, CS06, CS07,CS08,CS10,CS11,    CS12, 
                 CS13,CS14,CS15,CS17, CS18, CS19, CS20 ,CS21, CS22) %>% 
  rowwise() %>% 
  mutate(Total_communication = sum(across(starts_with("CS")), na.rm = T),
         F1 = sum(CS15,CS22,CS20,CS14,CS18,CS13,CS06,CS10),
         F2 = sum(CS19,CS04,CS17,CS12,CS08,CS07))

@@
